R Notebook

### 2017-11-13 modeling/modelAnalysis.Rmd
Fix numeric issue when there are -Infs

params <- read_delim('./bdaOutput/testingParams.csv', delim = ',')

@@

modelOutput = params %>%
  filter(prob != -Inf) %>%
  group_by(model) %>%
  summarize(prob = reduce(logLikelihood, sumlogprob) - log(length(logLikelihood)))

@@

?arrange
```

>>>>

params <- read_csv('./bdaOutput/testingParams.csv', col_types = c('cnnnnnnd'))#, delim = ',')

@@

modelOutput = params %>%
  #filter(logLikelihood != -Inf) %>%
  group_by(model) %>%
  summarize(logLikelihood = reduce(logLikelihood, sumlogprob) - log(length(logLikelihood)))

@@

```
